---
title: "poolseq-PCA"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Before you start
An allelic depth file is needed from a filtered VCF File. It can be obtained using the following:
```
bcftools query -H -f '%CHROM\t%POS\t%REF\t%ALT[\t%AD]\n' file.vcf > output.tsv
```

Next use the `DepthtoFreq.sh <filename>` command to convert the depth file to frequencies. 
- This script has been coded to do the job, however, it is not optimized yet. 
- If you have ideas you are welcome to improve it.  


## Including Code

```{r Preparing the file and calculating major allele frequencies}
allelicDepthTable<-read.table("M2018-DP100-AF-noINDEL-AD.tsv",sep = "\t",header = T,check.names = F)

nCols<-ncol(allelicDepthTable)
depths<-strsplit(allelicDepthTable[,5],",")
af_all<-c()
#for (i in depths) {
#  j=as.numeric(i)
#  af=j[1]/sum(j)
#  af_all<-c(af_all,af)
#}

#for (i in 5:nCols){
#  depths<-strsplit(allelicDepthTable[,5],",")
  
#}
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
